% ToDo: Add solutions to this sometime *after* the pset is due (ZG)

\subsection{Exercises}
\begin{problem}[Hungerford 2.7.10]
\label{prob:1.1}
Show that $S_n$ is solvable for $n\leq 4$ but $S_3$ and $S_4$ are not nilpotent.
\end{problem}

\begin{problem}[Hungerford 2.8.3]
\label{prob:1.1}
Show that if $N$ is a simple normal subgroup of a group $G$ and $G/N$ has a composition series, then $G$ has a composition series.
\end{problem}

\begin{problem}[Hungerford 2.8.9]
\label{prob:1.1}
Show that any group of order $p^2 q$ (for primes $p,q$) is solvable.
\end{problem}

\begin{problem}[Hungerford 5.1.1]
Let $F/K$ be a field extension. Show that
\begin{enumerate}
    \item $[F: K] = 1$ iff $F = K$.
    \item If $[F: K]$ is prime, then there are no intermediate fields between $F$ and $K$.
    \item If $u\in F$ has degree $n$ over $K$, then $n$ divides $[F: K]$.
\end{enumerate}
\label{prob:1.1}
\end{problem}

\begin{problem}[Hungerford 5.1.8]
\label{prob:1.1}
Show that if $u\in F$ is algebraic of odd degree over $K$, then so is $u^2$, and moreover $K(u) = K(u^2)$.
\end{problem}

\begin{problem}[Hungerford 5.1.14]
\begin{enumerate}
    \item If $F = \mathbb{Q}(\sqrt 2, \sqrt 3)$, compute $[F: \mathbb{Q}]$ and find a basis of $F/\mathbb{Q}$.
    \item Do the same for $\mathbb{Q}(i, \sqrt 3, \zeta_3)$ where $\zeta_3$ is a complex third root of 1.
\end{enumerate}
\label{prob:1.1}
\end{problem}

\begin{problem}[Hungerford 5.1.16]
Show that in $\mathbb{C}$, the fields $\mathbb{Q}(i) \cong \mathbb{Q}(\sqrt 2)$ as vector spaces, but not as fields.
\label{prob:1.1}
\end{problem}

\newpage
\subsection{Qual Problems}

\begin{problem}
Let $R$ and $S$ be commutative rings with multiplicative identity.

\begin{enumerate}
    \item Prove that when $R$ is a field, every non-zero ring homomorphism $\phi: R\to S$ is injective.
    \item Does (a) still hold if we only assume that $R$ is a domain? If so, prove it, and if not provide a counterexample.
\end{enumerate}
\end{problem}

\begin{problem}
Determine for which integers the ring $\mathbb{Z}/n\mathbb{Z}$ is a direct sum of fields. Carefully prove your answer.
\end{problem}

\begin{problem}
Suppose that $R$ is a commutative ring. Show that an element $r\in R$ is not invertible iff it is contained in a maximal ideal.
\end{problem}

\begin{problem}\hfill

\begin{enumerate}
    \item Give the definition that a group $G$ must satisfy the be solvable.
    \item Show that every group $G$ of order 36 is solvable.
    
    \textit{Hint: You may assume that $S^4$ is solvable.}
\end{enumerate}
\end{problem}
