\subsection{Exercises}

\begin{problem}[Hungerford 5.4.11]
Determine all subgroups of the Galois group and all intermedate fields of the splitting (over $\mathbb{Q}$) of the polynomial $(x^{3}-2)(x^{2}-3)\in \mathbb{Q}[x]$.
\end{problem}

\begin{problem}[Hungerford 5.4.12]
Let $K$ be a subfield of $\mathbb{R}$ and let $f \in K[x]$ be an irreducible quartic. If $f$ has exactly 2 real roots, the Galois group of $f$ is either $S_{4}$ or $D_{4}$.
\end{problem}

\begin{problem}[Hungerford 5.8.3]
Let $\phi$ be the Euler function.
\begin{enumerate}
    \item $\phi(n)$ is even for $n>2$.
    \item find all $n>0$ such that $\phi(n)=2$.
\end{enumerate}
\end{problem}

\begin{problem}[Hungerford 5.8.9]
If $n>2$ and $\zeta$ is a primitive n-th root of unity over $\mathbb{Q}$, then $[\mathbb{Q}(\zeta + \zeta^{-1}): \mathbb{Q}]=\phi(n)/2.$
\end{problem}

\begin{problem}[Hungerford 5.9.1]
If $F$ is a radical extension field of $K$ and $E$ is an intermediate field, then $F$ is a radical extension of $E$.
\end{problem}

\begin{problem}[Hungerford 5.9.3]
Let $K$ be a field, $f\in K[x]$ an irreducible polynomial of degree $n\geq 5$ and $F$ a splitting field of $f$ over $K$. Assume that $Aut_{k}(F)\simeq S_{n}$. Let $u$ be a root of $f$ in $F$. Then,
\begin{enumerate}
    \item $K(u)$ is not Galois over $K$; $[K(u):K]=n$ and $Aut_{K}(K(u))=1$ (and hence solvable).
    \item Every normal closure over $K$ that contains $u$ also contains an isomorphic copy of $F$.
    \item There is no radical extension field $E$ of $K$ such that $K\subset K(u)\subset E$.
\end{enumerate}
\end{problem}

% Qual Problems
\newpage
\subsection{Qual Problems}
\begin{problem}
\begin{enumerate}
    \item Let $K$ be a field. State the main theorem of Galois theory for a finite field extension L/K
    \item Let $\zeta_{43} := e^{2\pi i /43}$. Describe the group of all field automorphisms $\sigma : \mathbb{Q} (\zeta_{43})\rightarrow \mathbb{Q} (\zeta_{43})$.
    \item How many proper subfields are there in the field $\mathbb{Q} (\zeta_{43})$?
\end{enumerate}
\end{problem}

\begin{problem}
Let $F$ be a field and let $f(x)\in F[x]$.
\begin{enumerate}
    \item Define what is a splitting field of $f(x)$ over $F$.
    \item Let $F$ be a finite field with $q$ elements. Let $E/F$ be a finite extension of degree $n>0$. Exhibit an explicit polynomial $g(x)\in F[x]$ such that $E/F$ is a splitting of $g(x)$ over $F$. Fully justify your answer.
    \item Show that the extension $E/F$ in (2) is a Galois extension.
\end{enumerate}
\end{problem}

\begin{problem}
Let $K \subset L \subset M$ be a tower of finite degree field extensions. In each of the following parts, either prove the assertion or give a counterexample (with justification).
\begin{enumerate}
    \item If $M/K$ is Galois, then $L/K$ is Galois
    \item If $M/K$ is Galois, then $M/L$ is Galois.
\end{enumerate}
\end{problem}
