
\documentstyle{article}

\begin{document}
\noindent K. Lesh \hfill{23 Sept. 1995}\\
\noindent G. Thompson\\

\begin{center}
Topology Qualifying Exam
\end{center}

The Ph.D. qualifying exam committee tries to proofread the examinations as
carefully as possible.  Nevertheless, the exam may contain misprints.  If
you are convinced a problem has been stated incorrectly, mention this to the
proctor and indicate your interpretation in your solution. In such cases do not
interpret the problem in such a way that it becomes trivial.\\

\noindent Directions: Do four problems in each section. Budget your
time. Write your solution for each question on a separate page. \\

\noindent Section I
 
\begin{enumerate}

\item Let $A$ and $B$ be closed subspaces of a topological space $X$ 
        with  $X = A \bigcup B$. Suppose that $f: A \rightarrow Y$ and 
        $g: B \rightarrow Y$ are continuous, and $f(x)=g(x)$
        for all $x \in A \bigcap B$. 

\noindent Prove that $h: X \rightarrow Y$ by 
$$ h(x) = \left\{ \begin{array}{ccc}
            f(x)  & \mbox { if } & x \in A \\
            g(x)  & \mbox { if } & x \in B
          \end{array} \right. $$
is continuous. Is it necessary for both $A$ and $B$ to be closed?
Discuss.

\item Let $f : X \rightarrow Y$ by a quotient map. Let $Y$ be connected
and suppose that for each $y \in Y$, $f^{-1}(y)$ is connected. Prove
that $X$ is connected.

\item Let $I$ be a non empty index set, let 
$\{ X_{\alpha} | \alpha \in I \}$ be a family of topological spaces, and let
$A_{\alpha} \subseteq X_{\alpha}$ for each $\alpha$. 
      \begin{enumerate}
        \item Show that if $A_{\alpha}$ is closed in $X_{\alpha}$ for
              each $\alpha$, then $\prod A_{\alpha}$ is closed in 
              $\prod X_{\alpha}$.
        \item Show that ${\overline{\prod A_{\alpha}}} 
                      = \prod {\overline {A_{\alpha}}}$.
        \item Prove or disprove: If $A_{\alpha}$ is open in $X_{\alpha}$
              for each $\alpha$, then $\prod A_{\alpha}$ is open in 
              $\prod X_{\alpha}$.
       \end{enumerate}

\item Let $D$ be the closed unit disk in the complex plane. Let 
        $\sim$ be the equivalence relation on $D$ defined by 
        $z_{1} \sim z_{2}$ if and only if $z_{1} = z_{2}$ or 
        $|z_{1}| = |z_{2}| < 1$. Is the quotient
        topological space Hausdorff? (Prove your assertion.) 

\item State the definition of compactness for topological spaces. Prove
        {\underline{from}} {\underline{your definition}} 
        that the closed unit interval $[0,1]$ is compact.

\end{enumerate}

\newpage

\noindent Section II

\begin{enumerate}

\item Define what it means for $Y$ to be a strong deformation retract of
        $X$, where $Y \subseteq X$ are topological spaces. Prove that if
        $i : Y \rightarrow X$ is the inclusion map and $y \in Y$, then
        the induced homomorphism 
        $i_{*}: \pi_{1} (Y,y) \rightarrow \pi_{1} (X,y)$
        is an isomorphism.

\item Prove by any method you know that:
        \begin{enumerate}
            \item $\Re $ is not homeomorphic to $\Re^{2}$.
            \item $\Re^{2}$ is not homeomorphic to $\Re^{3}$.
        \end{enumerate}

\item Let $X_{1}$ and $X_{2}$ be two copies of $S^{2}$ and let $N_{1},
        S_{1}$ and $N_{2}, S_{2}$ be the north and south poles of $X_{1}$ and
        $X_{2}$, respectively. Define $X$ to be the quotient space obtained by
        identifying $N_{1}$ with $N_{2}$ and $S_{1}$ with $S_{2}$. Compute
        the fundamental group of $X$ by using the Seifert-van Kampen theorem.

\item \begin{enumerate}
        \item Define a covering space.
        \item State the main theorem about path lifting and covering
                spaces.
        \item Let $S^{1} \bigvee \Re P^{2}$ be the one point union of the
                circle and two dimensional real projective space, {\it i.e.}
                the quotient space obtained by taking the disjoint union
                of $S^{2}$ and $\Re P^{2}$ and then identifying a single point
                $x \in S^{2}$ with a single point in $ y \in \Re P^{2}$. 
                Describe the universal cover of $S^{1} \bigvee \Re P^{2}$.
        \item Describe the fundamental group of $S^{1} \bigvee \Re P^{2}$.
      \end{enumerate}

\item Prove that $\Re^{2}$ cannot be retracted to $S^{1}$. 
\end{enumerate}

\end{document}









