\documentclass[psamsfonts, 11pt, reqno]{amsart}
\setlength{\topmargin}{0pt}
\setlength{\footskip}{10pt}
\setlength{\oddsidemargin}{2.5cm}
\setlength{\evensidemargin}{2.5cm}
\setlength{\textwidth}{329pt}
\addtolength{\textheight}{50pt}
\usepackage{amsfonts,amsmath, amsthm, amssymb, latexsym, amscd, epsfig, pdfsync}
\usepackage[all]{xy}
\usepackage[mathscr]{eucal}
%\usepackage{layout}
%\addtolength{\topmargin}{-90pt}
%\addtolength{\textheight}{140pt}
\addtolength{\textwidth}{120pt}
\addtolength{\hoffset}{-60pt}
\everymath={\displaystyle}

\newcommand{\seriesk}{\sum\limits_{k=1}^{\infty}}
\newcommand{\seriesn}{\sum\limits_{n=1}^{\infty}}
\newcommand{\z}{\mathbb{Z}}
\newcommand{\n}{\mathbb{N}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\q}{\mathbb{Q}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\la}{\langle}
\newcommand{\ra}{\rangle}
\newcommand{\x}{\underline{\underline{x}}}
\renewcommand{\r}{\underline{\underline{r}}}
\renewcommand{\t}{\mathcal{T}}
\renewcommand{\d}{\mathcal{D}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\pic}{\mathbb{P}}
\newcommand{\p}{\mathcal{P}}
\newcommand{\Q}{\mathcal{Q}}
\newcommand{\ds}{\displaystyle}
\renewcommand{\tilde}{\widetilde}
\newcommand{\inv}{^{-1}}
\renewcommand{\oplus}{\bigoplus}
\renewcommand{\Sigma}{\sum}
\renewcommand{\Pi}{\prod}
\renewcommand{\phi}{\varphi}

\newtheorem{definition}{Definition}
\newtheorem{thm}[definition]{Theorem}
\newtheorem{theorem}[definition]{Theorem}
%\theoremstyle{definition}
%\newtheorem{fact}[defn]{Fact}
%\newtheorem{note}[defn]{Note}
\newtheorem{lemma}[definition]{Lemma}
%\newtheorem{cor}[defn]{Corollary}
%\newtheorem{conjecture}[defn]{Conjecture}
%\newtheorem{problem}[defn]{Problem}
%\newtheorem{notation}[defn]{Notation}
%\newtheorem*{question}{Question}
\newtheorem{ex}[definition]{Example}
\newtheorem{example}[definition]{Example}
%\newtheorem*{results}{Known Results}

\title{QualProblems}
%\author(,\\
%}

\begin{document}
\begin{center}
\begin{large}
Topology Qual Workshop Day 2: Connectedness and Path Connectedness
\end{large}
\end{center}
\vspace{.25in}

\begin{enumerate}
\item (June '08 \# A2) Let $p: X \rightarrow Y$ be a quotient map.  Show that if $Y$ is connected and moreover each set $p^{-1}(\{y\})$
is connected, then $X$ is connected.

\vfill

\item (Jan '08 \# B7) Show that if $A$ is a proper subset of a connected space $X$ and $B$ is a proper subset of a connected space $Y$,
then $(X \times Y) \setminus (A \times B)$ is connected.

\vfill

\item (June '07 \# A2) A space $(X, \mathcal{T})$ is called \emph{locally path-connected} if, for every $x \in X$, every neighborhood
of $x$ contains a path-connected neighborhood of $x$.  Show that a connected, locally path-connected space is path-connected.

\vfill

\item (Jan '06 \# A5) Recall that a topological space $X$ is \emph{locally connected} if for every point $x \in X$ and every
neighborhood $U$ of $x$ there exists a connected neighborhood $V$ of $x$ with $V \subseteq U$.
\begin{enumerate}
\item Prove that a topological space $X$ is localy connected iff for every open set $U\subseteq X$ the components of $U$ are open.
\item Now let $p: X \rightarrow Y$ be a quotient map.  Prove that if $C$ is a component of an open subset $U\subset Y$
then $p^{-1}(C)$ is a union of components of $p^{-1}(U)$.
\item Deduce that if $X$ is locally connected, then so is $Y$.
\end{enumerate}

\vfill

\item (June '05 \# A3) Let $X$ be a connected space with connected subset $Y$, and suppose that $X \setminus Y$ is not connected,
with $X \setminus Y = A \cup B$ a separation of $X \setminus Y$.  Show that if $B$ is open in $X$, then $A \cup Y$ is a connected
subset of $X$.

\vfill

\item (Jan '02 \# A3) Let $X$ be a topological space, and $A,B \subset X$ be connected subsets of $X$.  Show that if $A \cap \overline{B}
\neq \emptyset$ then $A \cup B$ is a connected subset of $X$.

\vfill

\item (Jan '02 \# A5) Show that $\mathbb{R}$ and $\mathbb{R}^2$ (with their usual topologies) are not homeomorphic.

\vfill

\item (June '10 \# A4) Let $Z = X \cup Y$, for $X$ and $Y$ connected subspaces of $Z$ with $X \cap Y = \emptyset$.  Let
$x_0 \in X$ and $y_0 \in Y$.  Let $\sim$ be the equivalence relation generated by the equivalence $x_0 \sim y_0$.  Show
that the quotient space $Z/\sim$ is connected.

\vfill

\item (Purdue '10) Prove or disprove: If $X$ is path connected, and $f: X \rightarrow Y$ is continuous, then $f(x)$ is
path connected.

\vfill



\end{enumerate}

\end{document}